Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-18 paper/ijcai/paper.tex
pass

\author{
First Author$^1$,
Second Author$^2$,
Third Author$^3$
\\ 
$^1$ First Affiliation\\
$^2$ Second Affiliation\\
$^3$ Third Affiliation\\
%
first@email.address,
second@email.address,
third@email.address
}

@@

\begin{abstract}
\Sof{@TODO}Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. It has survived not only five centuries, but also the leap into electronic typesetting, remaining essentially unchanged. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum. It was popularised in the 1960s with the release of Letraset sheets containing Lorem Ipsum passages, and more recently with desktop publishing software like Aldus PageMaker including versions of Lorem Ipsum.
\end{abstract}

@@

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic Slicing ~\citeauthor{Agrawal:1990:DPS:93542.93576} looks for the statements
in code that influence the evaluation of the fault-revealing
assertion. Although the technique has been intensively investigated in
research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
exception.  \sfl{}~\cite{7390282}, in contrast, does not try to
recover the influence region of faulty statements. It is a black-box~
statistical fault localization method that computes suspiciousness
values associated with program entities (e.g., basic blocks). For
that, it uses coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in decreasing
order of suspiciousness. Similarly to \ds{}, \sfl{} received
tremendous attention over the years, but its applicability to support
debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been
shown useful in supporting downstream analyses, such as Automated
Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for fixes to buggy
statements. Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes.

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, reported nearly 5
years ago, no tool or client analyses use this combination
today. Several reasons could justify that observation. One hypothesis is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranked statements, which is often a large
number. As such, it inflates actual improvements and deceives
potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact and encouraged researchers to adopt more precise metrics,
such as \topk{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first $k$ components.

@@

Spectrum-based fault localization (\sfl) is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
\emph{components}\footnote{A component can be any source code artifact
  of arbitrary granularity such as a class, a method, a statement, or
  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the coverage
of component $c_j$ in transaction $t_i$.  The pair $(\mathcal{A},e)$
is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{r}{0.29\textwidth}
  \vspace{-2ex}
  \hspace{-3ex}
  \centering
  \small
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

@@

To evaluate the impact of the \comb{} combination, the authors rcompare the cost of diagnosing faulty software programs using SFL against using \comb{} for top-5 and top-10 of classes.

@@

Following other recent studies, we used the \dfj{} benchmark in our
experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library
that provides a set of helper utilities for the {\small\texttt{java.lang}}
API. \cmath{} is a lightweight library of self-contained
mathematics and statistics components. The \closure{} is a toolset for
turning JavaScript files into smaller scripts for faster
download and execution in the browser. \chart{} is a library with a
full-featured charts user interface for Java. \jtime{} is a
lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is
a mocking testing framework.\comments{ that enables the developer to simulate
the behavior of classes that cannot be used in unit testing.}

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lccc}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}
\label{tab:df4j}
\end{table}
\normalsize

@@

To be able to effectively compare \comb{}-k against SFL, we first reduce the SFL report to method components. This reduction is done by considering the highest fault probability of the top-k components of each fault (/subject), to effectively be able to compare method-level diagnostic effort between the
two approaches. A variety in diagnostic effort is measured
using

@@

In \textbf{RQ1}, we pretend to evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.

>>>>

%% \author{
%% First Author$^1$,
%% Second Author$^2$,
%% \\ 
%% $^1$ First Affiliation\\
%% $^2$ Second Affiliation\\
%% %
%% first@email.address,
%% second@email.address,
%% third@email.address
%% }

@@

\begin{abstract}
  ...
\end{abstract}

@@

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
in code that influence the evaluation of the fault-revealing
assertion. Although the technique has been intensively investigated in
research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
exception. In contrast to \ds{}, \sfl{}~\cite{7390282} does not analyze
code. It is a black-box~
statistical fault localization method that computes suspiciousness
values associated with program entities (e.g., basic blocks). For
that, it uses coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in decreasing
order of suspiciousness. Similarly to \ds{}, \sfl{} received
tremendous attention over the years, but its applicability to support
debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been
shown useful in supporting downstream analyses, such as Automated
Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for fixes to buggy
statements. Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes.

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, no tool or client analyses use this combination
today.\Mar{$\leftarrow$ revise. inconsistent. there is a recent paper
  building on that idea...from 2018.} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranked statements, which is often a large
number. As such, it inflates actual improvements and deceives
potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact and encouraged researchers to adopt more precise metrics,
such as \topk{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first $k$ components.

@@

Spectrum-based fault localization (\sfl) is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in
fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
following are given in \sfl{}: a finite set $\mathcal{C} =
\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
  component can be any source code artifact of arbitrary granularity
  such as a class, a method, a statement, or a
  branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an
$N\times{}M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
coverage of component $c_j$ in transaction $t_i$.  The pair
$(\mathcal{A},e)$ is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{2}{0.3\textwidth}
  \hspace{-2ex}
  \centering
  \scriptsize
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

@@

%This section evaluates \comb{}.

@@

As in other recent related studies, we used the \dfj{} benchmark in
our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library that provides a set of helper utilities for the
     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
     of self-contained mathematics and statistics components. The
     \closure{} is a toolset for turning JavaScript files into smaller
     scripts for faster download and execution in the
     browser. \chart{} is a Java library for creating charts. \jtime{}
     is a lightweight library that aims to replace the default Java
     {\small\texttt{java.util.Date}} classes providing simpler
     APIs. \mockito{} is a mocking testing framework.\comments{ that
       enables the developer to simulate the behavior of classes that
       cannot be used in unit testing.}

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Mar{numbers seem too
    big. is this really in
    *k*LOC or just LOC? please, confirm.}}
\label{tab:df4j}
\end{table}
\normalsize

@@

The evaluation techniques are SFL and \comb{}-$k$, for
$k\in\{5,10\}$. \Mar{Simplified and moved this par. from Section
  4.0. I noticed you used this terminology (\comb{} with ``-k'')
  below. Please, explain and provide rationale}.

To be able to effectively compare \comb{}-k against SFL, we first reduce the SFL report to method components. This reduction is done by considering the highest fault probability of the top-k components of each fault (/subject), to effectively be able to compare method-level diagnostic effort between the
two approaches. A variety in diagnostic effort is measured
using\Mar{$\leftarrow$Sofia, I found this par. confusing.}

@@

In \textbf{RQ1}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.
